Technical Report

### 2017-11-08 fully-abstract-comp/technical-report.tex
comment
Remove some obsolete notes, add a new comment.

\lau{30-08-2017: We had $\rret$ as not being one of the registers on the source machine. I could not recall why we had this, so I removed it. (I think it may have been from when we had call and return instructions?)}
\dominique{26-9-2017: I think we should allow $\rstk$ in the source language too.}
\lau{28-09-2017: I can see from the commit history that this was something when we had push/pop instructions as well as a return instruction. I have removed the restriction on $\rstk$.}

@@

\dominique{27-09-2017: I think we need to do something about tail calls in the source language?}
\lau{27-09-2017: In what sense? Do you want to allow them (I do not think they are allowed at the moment?)}

>>>>

@@

\dominique{27-09-2017: I think we need to do something about tail calls in the source language?}
\lau{27-09-2017: In what sense? Do you want to allow them (I do not think they are allowed at the moment?)}
\dominique{8-11-2017: Yes, I would like to support them.  I think it would be a strength of our calling convention that we can support them (as I expect we can) and it would be good to demonstrate this.}
